Title

### 2023-05-03 main.tex
Corrección
Batman! (this commit has no parents)

In this section we propose a quantum circuit that simulates N-qubit Pauli
channels.  Furthermore, we show the results of implementing the circuit for
$N=1$ on a quantum computer.

To create the circuit, we remember that a Pauli channel as the one in eq.~(\ref{eq: pauli channel N-qubit})
applies each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
Given this, it is easy to construct a quantum circuit that implements 
a Pauli channel with the help of $2N$ ancilla qubits,
the circuit that does this is presented in fig. (\ref{fig: circuit-pauli}).
The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
\begin{eqnarray}
\label{eq: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
in the ancilla qubits, 
where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$.
The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined by $|\gamma_1 \rangle \cdots |\gamma_N\rangle$.

@@

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q:\; |0\rangle^{\otimes N}$} & \qw & \gate{\sigma_{\vec{\gamma}}} \gategroup[wires=2,steps
=1,style={dashed, inner sep=4pt}]{Repeat for all $\vec{\gamma}$}
\gategroup[wires=2,steps
=1,style={dashed, inner sep=4pt}, label style = {label position = below, yshift = 0.15cm}]
{$|\vec{\gamma}\rangle$} & \qw \\
\lstick{$\tilde{q}:\; |0\rangle^{\otimes 2N}$} & \gate[wires=1]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \ctrl{-1} 
% \gategroup[wires=1,steps
%=1,style={color=white, inner sep=0pt}, label style= {label position=below}]{$|\vec{\gamma}\rangle$} 
& \qw 
\end{quantikz}
\caption{\textbf{\tbnote{Hay que quitar esta imagen del texto al entregar el artículo y ponerla en un archivo a parte de tipo TIFF or EPS. Hay que dejar el figure solamente con la caption y label.}} {\bf Circuit for an $N$-qubit Pauli channel on $N$ qubits.}
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on the $2N$ ancilla qubits denoted by $\tilde{q}$. 
Then, for every vector $\vec{\gamma}$, it applies the operator $\sigma_{\vec{\gamma}}$ 
if the ancilla qubits are in the state $\vec{\gamma}$.}
\label{fig: circuit-pauli}
\end{figure}

This means that when measured in the computational basis, the state given in eq.~(\ref{eq: state})
collapses to $|\vec{\gamma}\rangle$ with a 
probability $|b_{\vec{\gamma}}|^2 = k_{\gamma}$. 
The circuit in fig.~(\ref{fig: circuit-pauli}) uses this fact
to operate $\sigma_{\vec{\gamma}}$ on the principal qubits
with a probability $k_{\gamma}$ by using controlled operations 
that apply $\sigma_{\vec{\gamma}}$ to the principal qubits
only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
Therefore, the circuit from fig.~(\ref{fig: circuit-pauli}) 
applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
with a probability $k_{\vec{\gamma}}$, 
just as a Pauli channel is supposed to do.  \\

\subsection{Simulation for one-qubit Pauli channels} % {{{
\label{subsec: Simulation for one-qubit Pauli channels}
For the particular case of a Pauli channel on one qubit, 
the circuit that simulates it can be constructed as in fig. (\ref{fig: citcuit-pauli-1}),
 which is a special case of fig. (\ref{fig: circuit-pauli})
 but with all qubits explicitly shown.

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
\lstick{$\tilde{q}_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
\lstick{$\tilde{q}_1$} & \gateinput{$\;\;\;\;\;b_0 |0 \rangle |0 \rangle + b_1 |0 \rangle |1 \rangle + b_2 |1 \rangle |0 \rangle + b_3 |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
\end{quantikz}
\caption{\tbnote{Al igual que antes, hay que adaptar esta figura y quitarla antes de entregar}. {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).}
\label{fig: citcuit-pauli-1} 
\end{figure}
Taking advantage of the quantum computers that IBM has available~\cite{Qiskit},
we sampled $249$ one-qubit Pauli channels and simulated them using the 
ibmq-lima quantum computer. 
For each of these channels, we used quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the
Choi matrix corresponding to the implementation of the circuit $\mathcal{C}_{I}$.
Then, we compared this Choi matrix with the theoretical
Choi matrix $\mathcal{C}_T$ of the channel we wanted to implement.

To make this comparison, we used the diamond norm~\cite{Aharonov},
which allows us to discriminate between quantum channels.
Suppose an agent is given one of the channels $\mathcal{C}_I$, $\mathcal{C}_T$
with probability $1/2$ for each,
and tries to guess which channel they received
by passing through it a state $\rho$ and measuring the result.
Then, the maximal probability of success (out of all possible states $\rho$) that
the agent guesses correctly is~\cite{Benenti}:
\begin{equation}
\label{eq: probability-success}
p_{succ} = \dfrac{1}{2}+ \dfrac{1}{2} ||\mathcal{C}_I - \mathcal{C}_T ||_{\diamond},
\end{equation}
where $|| \cdot ||_{\diamond}$ is the diamond norm.
Notice that $p_{succ}=1/2$ means that the channels
are indistinguishable, while $p_{succ}=1$
indicates that they are perfectly distinguishable.

Finally, using the representation of Pauli channels in a tetrahedron as
in eq.~(\ref{eq: conditions-tetrahedron}),
we show in fig.~(\ref{fig: fidelity one qubit}) the maximal probabilities of success defined by eq. (\ref{eq: probability-success}) for the channels analyzed.
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{probabilities-points.png}\\
\caption{\tbnote{Al igual que antes, hay que quitar esta figura y ponerla en un archivo a parte}. {\bf Maximal probabilities of success for one-qubit Pauli channel} $p_{succ}$ of one-qubit Pauli channels implemented on IBM's ibmq-lima. The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the distinguishability of each channel's implementation using the circuit for a 1-qubit Pauli channel.}
\label{fig: fidelity one qubit}
\end{figure}

\newpage
% }}}
% }}}
\section{OPR Circuits} % {{{
\label{sec: OPR Circuits}
Dynamical maps can be implemented using the same circuit as 
in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
to be created on the ancilla qubits depends on parameter $p$ 
and therefore is given by 
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}

>>>>

In this section we propose a quantum circuit that simulates $N$-qubit Pauli
channels.  Moreover, we implement the circuit for $N=1$ on a quantum computer
and analyze the results\cpnote{Quizá en una frase poner el resultado aca o ampliar
tantito}.

\cpnote{Yo abriría este parrafo con una frase que de la idea muy general. Decir 
algo asi como que vamos a crear un estado conque contenga a las $k$s 
como coeficientes y leugo controlar la aplicación de los Pauli strings. Luego
ya dar los detalles. Así incluso mas escueto de lo que pongo. Por ejemplo:
To design the circiot that implements 13, we construct a state that incorportes
probabilities $k$ and subsequently apply controlled operation. In particular... }
\cpnote{No me gusta como está organizado este parrafo. Le puedes dar una iterada?}
To design the circuit, we remember that a Pauli channel as the one in
eq.~(\ref{eq: pauli channel N-qubit})
applies each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
Given this, it is easy to construct a quantum circuit that implements 
a Pauli channel with the help of $2N$ ancilla qubits,
the circuit that does this is presented in fig. (\ref{fig: circuit-pauli}).
The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
\begin{eqnarray}
\label{eq: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
in the ancilla qubits, 
where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$.
The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined by $|\gamma_1 \rangle \cdots |\gamma_N\rangle$.

@@

\begin{figure}[h!]
\centering
% \begin{quantikz}
% \lstick{$q:\; |0\rangle^{\otimes N}$} & \qw & \gate{\sigma_{\vec{\gamma} }} \gategroup[wires=2,steps
% =1,style={dashed, inner sep=4pt}]{Repeat for all $\vec{\gamma}$}
% \gategroup[wires=2,steps
% =1,style={dashed, inner sep=4pt}, label style = {label position = below, yshift = 0.15cm}]
% {$|\vec{\gamma}\rangle$} & \qw \\
% \lstick{$\tilde{q}:\; |0\rangle^{\otimes 2N}$} & \gate[wires=1]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \ctrl{-1} 
% % \gategroup[wires=1,steps
% %=1,style={color=white, inner sep=0pt}, label style= {label position=below}]{$|\vec{\gamma}\rangle$} 
% & \qw 
% \end{quantikz}
\includegraphics{images/circuito_general.pdf}
\caption{\cpnote{Revisa el archivo images/circuito\_general.pdf y el makefile correspondiente} {\bf Circuit for an $N$-qubit Pauli channel on $N$ qubits.}
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on the $2N$ ancilla qubits denoted by $\tilde{q}$. 
Then, for every vector $\vec{\gamma}$, it applies the operator $\sigma_{\vec{\gamma}}$ 
if the ancilla qubits are in the state $\vec{\gamma}$.}
\label{fig: circuit-pauli}
\end{figure}

\cpnote{La primera frase es cierta, pero no le veo el sentido acá. Trata de reformular el parrafo 
de nuevo. Croe que el ``This means'' definitivamente no va y es el que le da un sentido ``raro''. 
Itera (quizá solo quitando esas dos palabras)}
This means that when measured in the computational basis, the state given in eq.~(\ref{eq: state})
collapses to $|\vec{\gamma}\rangle$ with a 
probability $|b_{\vec{\gamma}}|^2 = k_{\vec\gamma}$. 
The circuit in fig.~(\ref{fig: circuit-pauli}) uses this fact
to operate $\sigma_{\vec{\gamma}}$ on the principal qubits
with a probability $k_{\vec\gamma}$ by using controlled operations 
that apply $\sigma_{\vec{\gamma}}$ to the principal qubits
only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
Therefore, the circuit from fig.~(\ref{fig: circuit-pauli}) 
applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
with a probability $k_{\vec{\gamma}}$, 
just as a Pauli channel is supposed to do.  
\cpnote{Del circuito, parece ue las fases de las bs gammas no omportan mucho (o nada). 
Esa libertad la hemos considerado? De alguna manera colapsan curvas de las que
hemos visto?}

\subsection{Simulation for one-qubit Pauli channels} % {{{
\label{subsec: Simulation for one-qubit Pauli channels}
\cpnote{Es raro tener una sola subseccion. De perdida dos, o ninguna. Charlemso a ver como 
reorganizar las secciones (creo que el flujo si va bien hasta ahora)}

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in fig.~\ref{fig: citcuit-pauli-1},
 which is a special case of fig. \ref{fig: circuit-pauli}
 but with all qubits \cpnote{y compuertas , etc digamos que details} explicitly shown.

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
\lstick{$\tilde{q}_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
\lstick{$\tilde{q}_1$} & \gateinput{$\;\;\;\;\;b_0 |0 \rangle |0 \rangle + b_1 |0 \rangle |1 \rangle + b_2 |1 \rangle |0 \rangle + b_3 |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
\end{quantikz}
\caption{\cpnote{si quieres, intenta hacer la figura tu solo basado en el lo quehabía hecho. 
Otra cosa quizá para discutir. La creacion del estado especial de dos qubits no esta
aca explicita. Eso creo que si lo podemos hacer en general, o no? Como sería eso? Lo discutimos
a ver si lo pones?
} {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).}
\label{fig: citcuit-pauli-1} 
\end{figure}
Taking advantage of the quantum computers that IBM has available~\cite{Qiskit},
we sampled $249$ one-qubit Pauli channels and simulated them using the 
ibmq-lima quantum computer. 
For each of these channels, we used quantum process tomography~\cite{Qiskit,
Chuang:1996} to obtain the Choi matrix corresponding to the implementation of
the circuit $\mathcal{C}_{I}$ .
Then, we compared this Choi matrix with the theoretical
Choi matrix $\mathcal{C}_T$ of the channel we wanted to implement\cpnote{Quizá
referirnos mejor al canal? Lo discutimos}.

To perform this comparison, we used the diamond norm~\cite{Aharonov},
which allows us to discriminate \cpnote{creo qeu todas lasnormas nos
permiten discriminar entre canales. itera} between quantum channels.
Suppose an agent is given one of the channels $\mathcal{C}_I$, $\mathcal{C}_T$
with probability $1/2$ for each \cpnote{que pasa para una probabilidad $p$?
Otra cosa, los canales no se caracterizan por lo general po rla matriz 
de choi, tonces por aca quizá hay problemas. Discutamos notacion.},
and tries to guess which channel they received
by passing through it a state $\rho$ and measuring the result.
Then, the maximal probability of success (out of all possible states $\rho$) that
the agent guesses correctly is~\cite{Benenti}:
\begin{equation}
\label{eq: probability-success}
p_{succ} = \dfrac{1}{2}+ \dfrac{1}{2} ||\mathcal{C}_I - \mathcal{C}_T ||_{\diamond},
\end{equation}
where $|| \cdot ||_{\diamond}$ is the diamond norm.  Notice that $p_{succ}=1/2$
means that the channels are the same \cpnote{qioza una frase explicando porque
esto es razonable}, while $p_{succ}=1$ indicates that they are perfectly
distinguishable \cpnote{hummm ejemplo al menos para nosotros.}.

Finally, using the representation of Pauli channels in a tetrahedron as
in eq.~(\ref{eq: conditions-tetrahedron}),
we show in fig.~(\ref{fig: fidelity one qubit}) the maximal probabilities of
success defined by eq. (\ref{eq: probability-success}) for the channels
analyzed. \cpnote{Falta analisis de los resultados. }

\cpnote{Mejorar la figura, quizá dejando la tridimensional y ademas poniendo unos 6 cortes. Probar
con diferentes colores.}

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{probabilities-points.png}\\
\caption{\tbnote{Al igual que antes, hay que quitar esta figura y ponerla en un archivo a parte}. {\bf Maximal probabilities of success for one-qubit Pauli channel} $p_{succ}$ of one-qubit Pauli channels implemented on IBM's ibmq-lima. The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the distinguishability of each channel's implementation using the circuit for a 1-qubit Pauli channel.}
\label{fig: fidelity one qubit}
\end{figure}

% }}}
% }}}
\section{OPR Circuits} % {{{
\label{sec: OPR Circuits}
Dynamical maps can be implemented using the same circuit as 
in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
to be created on the ancilla qubits depends on parameter $p$ 
and therefore is given by 
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}
